Tidy Data

### 2014-01-17 tidy-data.tex
structural missingness

Table~\ref{tbl:preg-tidy} is the tidy version of Table~\ref{tbl:preg-raw-1}. Each row represents an observation, the \code{result} of one \code{treatment} on one \code{person}, and each column is a variable. We could also choose to drop the row containing the missing value, because missing values should only be omitted if they are structural, impossible because of the design of the experiment.

>>>>

Table~\ref{tbl:preg-tidy} is the tidy version of Table~\ref{tbl:preg-raw-1}. Each row represents an observation, the \code{result} of one \code{treatment} on one \code{person}, and each column is a variable. We might be tempted to drop the row containing the missing value. However, since missing values should only be omitted if they are structural (e.g., the number of pregnant men), doing so in this case would not be justified. It's an observation that should have been made.
